Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-06 paper/paper.tex
text

\section{Results}
\subsection{Frequency Dependent Optimizations}
- short description: get feeling for frequency range (by using unoptimized parameters
from the force paper), make optimizations with 3 different challenges: 1) challenges that cover the frequency area completely, challenges that cover low frequencies, and challanges that cover high frequencies, then pick genotypes with high fitness.
\subsection{Topology Optimizations}
Baseline
gain and feedback tests

@@

@@

\blindtext

>>>>

\section{Results}
\subsection{Frequency Dependent Optimizations}
- short description: get feeling for frequency range (by using unoptimized
parameters from the force paper), make optimizations with 3 different
challenges: 1) challenges that cover the frequency area completely,
challenges that cover low frequencies, and challenges that cover high
frequencies, then pick genotypes with high fitness.
\subsection{Topology Optimizations}
Baseline
gain and feedback tests

@@

\begin{figure}
    {\footnotesize\input{pictures/freq_optimization}}
    \caption{CAPTION TEXT}
    \label{fig:freqrange}
\end{figure}

@@

Our investigation showed that the frequency of the wave that is to be reconstructed 
strongly determines whether FORCE learning is able to learn that curve. Still, 
a good choice of network parameters is still able to improve the success rate for
certain frequency ranges. Some parameters ($p$, $feedback$) can vary in a relatively large interval
without influencing the success very much, whereas others are confined to a relatively small interval (gain).

The code developed for this paper provides a framework which can be used to perform a variety of similar 
investigations, e.g. the inclusion of feed forward topologies, or the extension to task other than simple 
sinusoidals. To that end, it would be wise to improve that selection algorithm by using the same tasks
for all generators in each generation, instead of evaluating them all independently. This would make the 
selection process more robust because it removes the dependence on the task distribution.

One problem with the approach presented here is that, in order to use the results of the genetic algorithm, 
we determined a single set of parameters by taking the mean of the values of the most successful generators, 
any information about an interdependence between the parameters is lost. We checked that there are no strong
correlations between any pair of parameters by doing 3D plots that showed the two parameters for each generator 
in development with the generations and could not detect any obvious correlation, but have not investigated 
this problem thoroughly.

The biggest problem with the current implementation, however, is the large amount of "magic" numbers, 
i.e. hyper-parameters of the optimization, that are used in the code. Their values were determined
by an informal search of testing a few optimizations. However, this should mostly affect the performance
of the optimization algorithm and not the results themselves.
